Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-03-16 paper.tex
update

To better understand that our evaluation approach could generate solutions having better semantic matchmaking quality with a slight trade off in $QoS$, we demonstrate an example solution to Task 3. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as two solutions employing QoS-aware approach and Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure while some service vertices and edges denoted in red are different. We list the semantic matchmaking quality represented by all edges ($e_1$ to $e4$) and overall QoS in Fig. \ref{comparisontest} $(3)$. To demonstrate how different the semantic matchmaking quality is, we analyse $e_4$ that has the smallest $\Delta Q$, which reveals the smallest semantic matchmaking quality gained using our approach. $e_4$ has two different source service vertices ($Ser1640238160$ and $Ser1947554374$) and two same $end$ vertices . Further more, in Fig. \ref{comparisontest} $(4)$, $Ser1640238160$ and $Ser1947554374$ are service with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' required outputs.
\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.22]{comparisontest.pdf}}}
 \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
 \label{comparisontest}
\end{figure}

>>>>

To better understand that our evaluation approach could generate solutions having better semantic matchmaking quality with a slight trade-off in $QoS$, we demonstrate an example solution to Task 3. Fig. \ref{comparisontest} $(1)$ and $(2)$ are two weighted DAGs as best solutions found employing QoS-aware approach and Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure while some service vertices and edges denoted in red are different. We list the semantic matchmaking quality represented by all edges ($e_1$ to $e4$), overall semantic matchmaking quality and QoS in Fig. \ref{comparisontest} $(3)$. To demonstrate how different the semantic matchmaking quality is, we analyse $e_4$ that has the smallest $\Delta Q$, which reveals the gain (positive $\Delta Q$) or loss (negative $\Delta Q$) for the listed qualities using our approach. The $e_4$ has two different source service vertices ($Ser1640238160$ and $Ser1947554374$) and the same $end$ vertices in two solutions. The outputs of two different source service are marked on the related taxonomy in Fig. \ref{comparisontest} $(4)$, $Ser1640238160$ and $Ser1947554374$ are service with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' required outputs.
\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.22]{comparisontest.pdf}}}
 \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
 \label{comparisontest}
\end{figure}
